Verifying Demonstrations

### 2019-02-28 paper/adversary-model.tex
Fixes missing punctuation
Changes time-stamping and storage to ledger, fixes #176

There are three players: the protester (with identity) \(P\), a witness (with 
identity) \(W\) and the time-stamping storage \(\TS\) (that will contain the 
set of all proof shares, \(\pshs\)).
The protester \(P\) and the witness \(W\) communicate some protocol data,
\(d_{P,W}(\cid, P)\), and records when the communication occurred \(t_{P,W}\).
The protester \(P\) communicates with \(\TS\), in which \(\TS\) only learns 
some function of the protocol data exchanged with the witness, 
\(f(d_{P,W}(\cid, P))\) for some function \(f\), and the time of the 
communication (\(t_{P,\TS}\)).
This is illustrated in \cref{fig:base-adversary}.

@@

The adversary maliciously controls \(W\).
The adversary honest-but-curiously controls \(\TS\), but can submit to \(\TS\) 
as everyone else.
The adversary only learns the protocol data --- \ie what is sent over the 
channel, no auxiliary data\footnote{%
  By auxiliary data we mean any data outside of the protocol, \ie
  meta-data such as who is on the other side of the channel obtained
  as side information, \eg by face recognition or inference from address
  to identity.
}

>>>>

There are three players: the protester (with identity) \(P\), a witness (with 
identity) \(W\) and a ledger~\(\TS\) (\ie time-stamping storage, that will 
contain the set of all proof shares, \(\pshs\)).
The protester \(P\) and the witness \(W\) communicate some protocol data,
\(d_{P,W}(\cid, P)\), and records when the communication occurred \(t_{P,W}\).
The protester \(P\) communicates with \(\TS\), in which \(\TS\) only learns 
some function of the protocol data exchanged with the witness, 
\(f(d_{P,W}(\cid, P))\) for some function \(f\), and the time of the 
communication (\(t_{P,\TS}\)).
This is illustrated in \cref{fig:base-adversary}.

@@

The adversary maliciously controls \(W\).
The adversary honest-but-curiously controls \(\TS\), but can submit to \(\TS\) 
as everyone else (\ie a malicious protester~\(P\)).
The adversary only learns the protocol data --- \ie what is sent over the 
channel, no auxiliary data\footnote{%
  By auxiliary data we mean any data outside of the protocol, \ie
  meta-data such as who is on the other side of the channel obtained
  as side information, \eg by face recognition or inference from address
  to identity.
}.
